\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax 


\chapter*{Acknowledgments}

I would like to begin by thanking my advisor Neil Shephard not only
for his support throughout the process of writing this thesis, but
also for the tremendous impact he has had on me during my undergraduate
career at Harvard. Neil's teaching over the years inspired in me a
deep interest in the relationship between statistics, mathematics,
and economics; the influence of the ideas he exposed me to on my personal
and intellectual growth could hardly be overstated.

I would also like to thank to Natesh Pillai for several helpful discussions
related to this thesis. In addition, I would like to thank my mentors
at the various firms I have worked at over my summers for making tangible
the links between what I was learning in school and the world as it
really is. I am also indebted to Scott Kominers, who showed me what
great research looks like, and gave me an opportunity to feel just
how exhilarating it could be to wrangle with ideas that I was truly
excited about.

I would further like to acknowledge the Odyssey cluster supported
by the Research Computing Group in the FAS Division of Science at
Harvard University, and the Research Computing Environment supported
by the Institute for Quantitative Social Science at Harvard University,
on which the computations in this thesis were performed.

Next, I would like to thank my blockmates Ramon Galvan and Anita Lo
for being the best of friends since our very first day at Harvard.
Our countless conversations in our dining hall have had and continue
to have a profound impact on how I see the world. I would also like
to thank Spencer Kwon, who inspired me in my sophomore year to push
into academic territory I never thought I would reach, and James Ho,
my fellow adventurer from the top of Mount Baker, along the Dotonbori
canal, to the bottom of the Florida Bay. And of course, I would like
to thank Alice Zhao, without whom I may have never returned to the
second lecture of the class that began my journey to this thesis,
and without whom the second half of college would have been a very
different two years indeed.

Finally, I would like to sincerely thank my parents for always doing
everything in their power to allow me to explore my interests without
limit. The absolutely caring and nurturing environment they created
is the major reason that I and my little brother are where we are
today, and I hope it will also be what leads Jack, if he chooses,
to one day write a thesis that far surpasses this one. 

\endgroup
